Behavior Driven Development in Haskell

### 2012-05-30 paper.tex
Make acks more concise (@kazu, yes, I agree)

We are grateful to David Waern, Haddock's maintainer, for reviewing our patches
and accepting our patches to Haddock.

\begin{quote}
  kazu: this seems redundant: how about "\emph{for reviewing and accepting our patches}"?
\end{quote}

>>>>

We are grateful to David Waern, Haddock's maintainer for reviewing and
accepting our patches to Haddock.
